\newpage

\section{Ethics}
\subsection{Ethical requirements}

\begin{itemize}
\item No human or animal ethical concerns have been identified for this study.
\end{itemize}


\subsection{Legal and intellectual property requirements}
Intellectual property requirements have been identified and are as follows:

\begin{itemize}

\item Historical basal site data under the custodianship of Department of Environment Parks and Water Security (DEPWS) will be used, the Executive Director of Rangelands Division (DEPWS) has approved the use of this data providing that appropriate citation is incorporated.

  \item Products derived from Landsat data by the Joint Remote Sensing Research Program (JRSRP), RSC and RSU will be used, these data-sets are publicly available; as such, no approvals are required to use these products providing that appropriate citations are incorporated.
  
  \item WFPC product derived by Dr. Grant Staben will be used \citep{stabenetal2018}, Dr. Staben has approved the use of this published model providing that the appropriate citation is incorporated.

  \item CH product derived by Dr. Grant Staben will be used \citep{staben2016}, Dr. Staben has approved the use of this published model product providing that the the appropriate citation is incorporated.
  
  \item Some python scripts have been derived by the Remote Sensing Unit, Rangelands Division (DEPWS). All scripts contain an MIT License agreement, allowing for use the scripts without restriction, product providing that appropriate citation are incorporated.
  
  
\end{itemize}